Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-05-26 article/05_Conclusion.Rmd
phrasing

4. Abolishing the separation into artificial regions for the cultural distance and correlation analysis in favour of an approach based on individual observations [@loogEstimatingMobilityUsing2017].

>>>>

4. Abolishing the separation into artificial regions for the cultural distance and correlation analysis in favour of an approach based on individual observations [e.g. @loogEstimatingMobilityUsing2017].
